The Controlled Choice Design and Paternalism in Pawnshop Borrowing

### 2023-07-25 donde.tex
introduce NA in causal RF

The combination of voluntary and forced commitment within the RCT allows us to address several key questions. First, do structured repayment contracts lower financial costs for pawnshop borrowers? Second, do borrowers recognize this benefit, demanding commitment in sufficient numbers?  Finally, and most uniquely given the presence of a forced commitment arm, we are able to ask whether the \textit{right} borrowers voluntarily demand commitment. In particular, we use the choice, control, and fored arms to point identify the Treatment on the Treated (TOT) and the Treatment on the Untreated (TUT) effects, along with the average selection on gains (ASG) and average selection bias (ASB).

@@

A less critical form of attrition would be a differential refusal to answer the survey questions.  The survey was done before treatment status was revealed, and we observe loan outcomes regardless of whether the survey was conducted.  Our core experimental estimates do not use the survey data as covariates, but the Random Forest analysis is restricted to the subset of borrowers who answered at least some survey questions. The top row of Table \ref{attrition_table} shows that the survey response rate is broadly similar across arms (about 77 percent). We can also examine differences in the fraction of borrowers who do respond to the survey and then do not end up taking a loan subsequent to completing the survey, we find that the share is close to as is the fraction of those 97\% across arms (p-value=\hl{XXX}).\footnote{We also tested if the number of pawns per day for the 6 branches that participated in the experiment was different 1 month before the experiment started or 1 month after the experiment ended, relative to the days the experiment was active. To this end we estimated the regression\footnote{We cluster the standard errors by branch.} $Pawns \: per \: day_{jt} = \alpha_j + \gamma f(t) + \beta_b \mathbbm{1}(t \in MB)_{t} +\beta_a \mathbbm{1}(t \in MA)_{t}$, where $\alpha_j$ are branch fixed effects, $f(t)$ is a third degree polynomial in time, $\beta_b$ measures a level effect in the number of pawns per branch a month before the experiment started, and $\beta_a$ a month after. We estimate no difference in the number of pawns, showing that people are not leaving the branch without pawning at larger rates during the experiment ($\beta_a=1.32$, $\beta_b=-0.65$, with p-values 0.11 and 0.83, respectively).  Table \ref{num_pawns_bal} shows the beta coefficients from these regressions, which are nowhere significant.}  Hence while survey response was not universal, there is no evidence that it was differential across arms.

@@

\todo[inline]{Add a column with losing pawn. What about re-pawning?}
\todo[inline]{How did we decide to deal with censoring?}

@@

\paragraph{Other costs.} We have shown that forcing borrowers to take the monthly payment contract significantly reduces financial cost. Although the paper focuses on financial cost, we consider three additional costs here. First, We include the cost of going to the branch. This includes the self-reported transport cost (most use public transport), as well as the opportunity cost of time. To err on the conservative side, we subtract a whole day's minimum wage the day of the visit, instead of just the wage corresponding to a couple of hours. Second, we consider a rough proxy of the value of liquidity they lose by paying earlier. We act as if each payment they make comes from an additional loan they take, which incurs interest at the same rate as Lender P's loan (7\% per month). So far we have valued the collateral at the gold value appraised by the lender, but the piece may be worth more to the borrower than its gold value.  For many of them the pawned jewelry has sentimental value as well. This is reflected in the subjective valuation they reported in the survey which is \hl{XXX\%} higher on average. Our third extra cost considers this higher value.

@@

\todo[inline]{I think the re-pawn table should only have 4 columns. Remove variables 3,4, and 7. In terms of the order: keep column 1, make 5 and 6  the new columns 2 and 3, and make the current column 2 the new column 4. I am goint to write the paragraphs assuming this.}

@@

The results from Section \ref{experiment} show that commitment \emph{works}: clients who were assigned to the forced commitment arm experienced substantially lower financial costs on average.
In spite of this, given the opportunity, only \hl{11\%} of borrowers chose commitment. 
If the effect of commitment were homogeneous, this would be enough to conclude that the \hl{89\%} who did not choose it would have been financially better-off if they had.
In a world of heterogeneous treatment effects, however, low demand for commitment could still be consistent with \textcolor{blue}{standard rational borrowers.}
The borrowers who did not choose commitment could simply be those who don't need it. 
Indeed, we find strong evidence that the effect of forced commitment varies substantially across individuals in our experiment: Appendix \ref{append:chernozhukov} tests and rejects the null hypothesis of homogeneous treatment effects, following the methodology of \cite{chernozhukov2018generic}.
So the question remains: do the \hl{89\%} who do not choose commitment know something about their personal situations that we as researchers do not, or are most people in the choice arm making a costly mistake? 
In this section we present a number of econometric exercises that shed light on this question, leveraging unique features of our experimental design. 
Despite substantial treatment effect heterogeneity, most borrowers would experience lower financial costs under a commitment contract. 
Indeed, commitment lowers average financial costs even for the subset of borrowers who would \emph{not} choose to commit voluntarily.
To simplify the exposition in this and all sections that follow, we re-define all outcome variables so that \emph{beneficial} treatment effects are \emph{positive}. Using this convention, a positive treatment effect of commitment on financial cost, for example, reflects the average cost \emph{savings} caused by commitment.

\subsection{Bounding the Distribution of Individual Treatment Effects}
\label{sec:bounds}

If we knew the distribution of individual treatment effects, it would be easy assess how many individuals would win and lose under a policy of universal forced commitment, along with the magnitude of any individual harm. 
Because we can never simultaneously observe the same borrower in both the control and commitment arms, however, the distribution of individual treatment effects cannot be point identified.
It can, however, be bounded.
We begin our exploration of heterogeneous treatment effects by computing assumption-free bounds on the share of individuals who benefit from forced commitment.

@@

@@

\section{Examining paternalism}
\label{exploring}

\subsection{Why is paternalism working in this context?}
\label{why_paternalism}

@@

\paragraph{Learning.} A first explanation involves learning. Our experiment introduced a new contract into an environment that had not previously featured commitment; perhaps clients required experience to understand its benefits. Given the strongly positive impact of forcing, this explanation would suggest that clients who were forced once would subsequently choose commitment if given the chance to do so. A subset of \hl{240 clients} from our experiment who were exposed to the experiment in one round and then returned to take another loan at a branch where the choice of commitment was offered.  Table \ref{learning_table} shows the results of this analysis.  While this regression is underpowered, given the small sample size, the point estimate on prior assignment to the commitment contract is actually negative. Hence the window available to us on learning provides little comfort that the lack of voluntary compliance is simply a matter of inexperience with commitment.\footnote{\textcolor{blue}{Risk could be another alternative potential explanation for low take up of the commitment contract. Appendix \ref{App_FOSD} shows however that the distribution of financial cost savings of the monthly payment contract first-order stochastically dominates that of the status quo contract, so that (assuming these are the distributions faced by borrowers) the former should be preferred by borrowers regardless of their degree of risk aversion. See the Appendix for more details.}}

\paragraph{Time discounting.} Discounting is a second potential explanation for our results.  Our estimated decrease in the financial cost of credit from above ignores discounting, but the intervention inherently imposes up-front costs (early payment) in return for delayed benefits (recovery of pawn).  Highly impatient individuals might therefore rationally choose the \emph{status quo} contract, despite our results showing a benefit raw (undiscounted) returns.  To investigate this explanationwe can calculate the Net Present Value of the $TUT$ on financial cost given the timing of repayment and pawn recovery for different hypothetical discount rates. Figure \ref{fc_discount_rates} presents the results of this exercise. We see that non-choosers continue to experience significant decreases in NPV financial costs up to annual discount rates of 4,000\%, and the NPV remains negative, although not significant, at 10,000\% discount rates.  As such, discounting is unlikely to explain why those who benefit, on average, from commitment fail to choose it when offered.

\paragraph{Present bias.} If commitment benefits among non-choosers cannot be explained by rational choice, the canonical behavioral story would center on time inconsistency.  While commitment is useful to anyone with hyperbolic time preferences, only those who are sophisticated--i.e.\ aware that they are hyperbolic discounters--will demand it.  A large share of naive hyperbolics in the population could therefore drive a large and positive $\text{TUT}$.  Our baseline survey included standard questions about discount rates between today and a month in the future versus discount rates between three and four months in the future.\footnote{The remaining exercises in the paper require information from the intake survey, and hence use only the subset of individuals who responded to the survey.  While this is a selected sample, estimates of the ATE, TOT, and TUT are nearly identical whether computed from the full sample survey-respondent sub-sample.}  This allows us to classify borrowers who display more impatience over immediate delays as time inconsistent.  This measure of financial hyperbolicity is widely used in survey research, although it is not without problems.\footnote{Our measure is dichotomous, and it is not incentivized. Recent empirical work has shown the superiority of more elaborate measures such as ``convex time budgets'' \citep{andreoni2015measuring} while questioning the interpretation of measures of hyperbolicity that are not based on consumption \citep{andreoni2012estimating, cohen2020measuring}, suggesting that real effort tasks provide a better measure \citep{augenblick2015working}.  Given that we had only a few minutes to interview real pawnshop clients prior to a commercial transaction, our simple measure was a necessary compromise.}

If we could perfectly measure hyperbolicity, we could divide the sample into three groups: sophisticated hyperbolics who chose commitment, time-consistent non-chooser for whom forcing will not be effective, and naive hyperbolic non-choosers for whom it will. If hyperbolic discounting fully explains the low take-up rate of voluntary commitment, this would imply that the forcing effect should arise entirely from hyperbolic non-choosers. If our survey measure divides borrowers into the correct groups, this implication can be checked by estimating the $\text{TUT}$ conditional on hyperbolicity.

For any binary pre-treatment covariate $X_i$, we can calculate the relative contributions of any two groups $X_i=0$ or $X_i=1$ to the overall $\text{TUT}$ effect using the following decomposition: 
\begin{align}
        1=& \frac{\mathbbm{E}[Y_{1i}-Y_{0i} | C_i=0, X_i=1]}{\text{TUT}}\mathbbm{P}(X_i=1 | C_i=0) \\
        \quad &+ \frac{\mathbbm{E}[Y_{1i}-Y_{0i}| C_i=0, X_i=0]}{\text{TUT}}\mathbbm{P}(X_i=0 | C_i=0)
        \label{eq:decomp}
\end{align}
where $\text{TUT}$ is the overall TUT effect and $\mathbbm{E}[Y_{1i} - Y_{0i}|C_i = 0, X_i = x]$ is the TUT conditional on $X_i = x$.    
If, as the behavioral theory outlined above would predict, the $\text{TUT}$ arises solely from hyperbolics then term with $X_i=1$ the former term will be one and the term with $X_i = 0$ will be zero.

\paragraph{Sure confidence.} A second behavioral explanation may arise from the fact that  74\% of the control participants believe they have a 100\% chance of recovering their pawn, while in truth only \hl{56\%} will do so.  This suggests a market characterized by over-optimism.  Incorrect expectations about recovery probabilities can explain low take-up in that individuals who believe they will repay are rationally uninterested in incurring costs to induce repayment.  Hence over-optimistic expectations in recovery probabilities will translate directly into under-adoption of preventive measures.   Similar to the definition of hyperbolicity above, we define a binary attribute we call ``sure-confidence.'' This measure equals one for any individuals who say at the time of borrowing that they have a 100\% probability of recovering their pawn. The same decomposition that we used above in our discussion of hyperbolic discounting, \eqref{eq:decomp}, can be used to explore the extent to which sure confidence explains our positive and significant TUT estimate by redefining the covariate $X_i$.

@@

Figure \ref{tut_beh_partition} shows the relative contributions of present bias and sure-confidence for the $TUT$.  In each figure the orange bar represents the contribution from those who do not possess the attribute, and the blue bar from those that do.  We see that the forcing effect is localized mostly to those who are \textit{not} time inconsistent, contradicting naive hyperbolicity as the justification for paternalism.  Instead, we see sure-confidence being a category that completely isolates the $TUT$, suggesting that forcing works for those who do not consider repayment structure because they don't think they need it.  Our measure of hyperbolicity is based on unincentivized responses in a short survey and so is likely to be noisy; nonetheless we see no evidence here that it drives the forcing effect.  Rather, this analysis suggests that paternalism is effective in this case is because of a group of overconfident borrowers who, heedless of the possibility of default, do not choose commitment and yet would benefit substantially from receiving it.

If the attribute of ``sure confidence'' proves so important in explaining the TUT, what are the determinants of this characteristic?  In Figure \ref{determinants_sure} we plot the coefficient estimates from a regression that explains sure confidence with a battery of individual-level characteristics.  Older males are more likely to be sure confident, as are those with more education.  Taken at face value, it also appears to be the case that it is those with less financial stress, those who have had less trouble paying bills, and those more relied upon financially by family members.  However, through a behavioral lens it is also possible that the type of person who is over-confident in their ability to repay a loan is also maintaining financial fictions in other domains of life, providing answers to the baseline survey questions that exaggerate their degree of economic security.  In any case it appears that this attribute may be difficult to target with objective demographic criteria, a point to which we return.

@@

@@

 Figure \ref{choose_wrong}, Panel A shows the results of this exercise, reinforcing the general superiority of commitment.  Among choosers, only 25\% would have had superior outcomes had they not complied, whereas among non-choosers almost 80\% made a mistake according to this definition.  Because this arm is comprised of 89\% non-choosers, the overall rate of mistake in the arm was around 70\%.  As we increase the threshold on the size of the mistake necessary to be classified as having made the wrong choice, by definition the share in both groups falls, and among choosers the number making an error falls quite quickly to zero.

@@

Panel C of this figure replicates this exercise for the forced commitment arm, with the difference being that the relevant treatment effect to match is now the ATE of the forced commitment arm.  This allows us to identify the winners and losers from paternalism in a nuanced manner, since members of groups with CATEs$<$0 are hurt and everyone else is helped.  Because the ATE$>$TUT, this exercise results in an even larger fraction of individuals benefiting from commitment; here we find that fully 87\% of individuals are better off being forced into commitment than staying in the control. This now allows us to make a stronger statement in favor of paternalism; not only is the case that forcing commitment generates large benefits on average, but it is also generating benefits for almost 90\% of the forced population.

@@

\begin{table}[H]
\caption{Main treatment effects}
\label{main_impact_table}
\begin{center}
\scriptsize{\input{./Tables/decomposition_main_te.tex}}
\end{center}
\scriptsize This table shows the treatment effects for our core pecuniary outcomes. Columns (1) \& (7) analyses this core measure. Further columns decomposes the core measure in all of its components, according to the different costs we measure :

@@

Each regression includes branch and day-of-week FE. Standard errors are clustered at the branch-day level.

@@

>>>>

The combination of voluntary and forced commitment within the RCT allows us to address several key questions. First, do structured repayment contracts lower financial costs for pawnshop borrowers? Second, do borrowers recognize this benefit, demanding commitment in sufficient numbers?  Finally, and most uniquely given the presence of a forced commitment arm, we are able to ask whether the \textit{right} borrowers voluntarily demand commitment. In particular, we use the choice, control, and forced arms to point identify the Treatment on the Treated (TOT) and the Treatment on the Untreated (TUT) effects, along with the average selection on gains (ASG) and average selection bias (ASB).

@@

A less critical form of attrition would be a differential refusal to answer the survey questions.  The survey was done before treatment status was revealed, and we observe loan outcomes regardless of whether the survey was conducted.  Our core experimental estimates do not use the survey data as covariates, but the Random Forest analysis is restricted to the subset of borrowers who answered at least some survey questions. The top row of Table \ref{attrition_table} shows that the survey response rate is broadly similar across arms (about 77 percent). We can also examine differences in the fraction of borrowers who do respond to the survey and then do not end up taking a loan subsequent to completing the survey, we find that the share is close to as is the fraction of those 97\% across arms (p-value=\hl{XXX}).%\footnote{We also tested if the number of pawns per day for the 6 branches that participated in the experiment was different 1 month before the experiment started or 1 month after the experiment ended, relative to the days the experiment was active. To this end we estimated the regression. We cluster the standard errors by branch.} $Pawns \: per \: day_{jt} = \alpha_j + \gamma f(t) + \beta_b \mathbbm{1}(t \in MB)_{t} +\beta_a \mathbbm{1}(t \in MA)_{t}$, where $\alpha_j$ are branch fixed effects, $f(t)$ is a third degree polynomial in time, $\beta_b$ measures a level effect in the number of pawns per branch a month before the experiment started, and $\beta_a$ a month after. We estimate no difference in the number of pawns, showing that people are not leaving the branch without pawning at larger rates during the experiment ($\beta_a=1.32$, $\beta_b=-0.65$, with p-values 0.11 and 0.83, respectively).  Table \ref{num_pawns_bal} shows the beta coefficients from these regressions, which are nowhere significant.}  Hence while survey response was not universal, there is no evidence that it was differential across arms.

@@

@@

\paragraph{Other costs.} We have shown that forcing borrowers to take the monthly payment contract significantly reduces financial cost. Although the paper focuses on financial cost, we consider three additional costs here. First, we include the cost of going to the branch. This includes the self-reported transport cost (most use public transport), as well as the opportunity cost of time. To err on the conservative side, we subtract a whole day's minimum wage the day of the visit, instead of just the wage corresponding to a couple of hours. Second, we consider a rough proxy of the value of liquidity they lose by paying earlier. We act as if each payment they make comes from an additional loan they take, which incurs interest at the same rate as Lender P's loan (7\% per month). So far we have valued the collateral at the gold value appraised by the lender, but the piece may be worth more to the borrower than its gold value.  For many of them the pawned jewelry has sentimental value as well. This is reflected in the subjective valuation they reported in the survey which is \hl{XXX\%} higher on average. Our third extra cost considers this higher value.

\todo[inline]{@Isaac, from Enrique: I would like to understand the liquidity adjustment better.}

@@

@@

The results from Section \ref{experiment} show that commitment \emph{works}: clients who were assigned to the forced commitment arm experienced substantially lower financial costs on average.
In spite of this, given the opportunity, only \hl{11\%} of borrowers chose commitment. 
If the effect of commitment were homogeneous, this would be enough to conclude that the \hl{89\%} who did not choose it would have been financially better-off if they had.
In a world of heterogeneous treatment effects, however, low demand for commitment could still be consistent with borrowers adhering to a standard model of rational choice. 
The borrowers who did not choose commitment could simply be those who don't need it. 
Indeed, we find strong evidence that the effect of forced commitment varies substantially across individuals in our experiment: \ref{append:chernozhukov} tests and rejects the null hypothesis of homogeneous treatment effects, following the methodology of \cite{chernozhukov2018generic}.
So the question remains: do the \hl{89\%} who do not choose commitment know something about their personal situations that we as researchers do not, or are most people in the choice arm making a costly mistake? 
In this section we present of econometric exercises that shed light on this question, leveraging unique features of our experimental design. 
Among other results, we show that commitment lowers average financial costs even for the subset of borrowers who would \emph{not} choose to commit voluntarily.
To simplify the exposition in this and all sections that follow, we re-define all outcome variables so that \emph{beneficial} treatment effects are \emph{positive}. Using this convention, a positive treatment effect of commitment on financial cost, for example, reflects the average cost \emph{savings} caused by commitment.

\subsection{Bounding the Distribution of Individual Treatment Effects}
\label{sec:bounds}
If we knew the distribution of individual treatment effects, it would be easy assess how many individuals would win and lose under a policy of universal forced commitment, along with the magnitude of any individual harm. 
Because we can never simultaneously observe the same borrower in both the control and commitment arms, however, the distribution of individual treatment effects cannot be point identified.
It can, however, be bounded.
We begin our exploration of heterogeneous treatment effects by computing assumption-free bounds on the share of individuals who benefit from forced commitment.

@@

The bounds we have just described are constructed by considering all possible joint distributions of $Y_0$ and $Y_1$ that are compatible with the observed marginal distributions $F_1$ and $F_0$. 
With stronger assumptions, it is possible to say more.
One such assumption is \emph{rank invariance}, which posits that a person's rank in the distribution of $Y_0$ equals her rank in the distribution of $Y_1$.
While strong, this assumption or variants of it has appeared in a number of settings in the literature, e.g.\ \cite{chernozhukov2005iv}. 
Under rank invariance, the distribution of treatment effects is point identified and given by 
\[
F_\Delta(\delta) = \int_0^1 \mathbbm{1}\{ F_1^{-1}(u) - F_0^{-1}(u)\leq \delta\}\,\mathrm{d}u 
\]
where $F_1^{-1}$ and $F_0^{-1}$ are the quantile functions of $Y_1$ and $Y_0$.
As we show in Appendix \ref{App_FOSD}, $Y_1$ first-order stochastically dominates $Y_0$ in our experiment: every quantile of the distribution of financial cost savings under forced commitment is higher than the corresponding quantile under the control condition, and the same is true for the APR outcome.
Since this implies that $F^{-1}_1(u) - F^{-1}_0(u)$ is always positive, rank invariance yields an extremely stark conclusion: all borrowers benefit from forced commitment. 
\todo[inline]{@Everyone: do we want to plot the distribution of treatment effects under rank invariance and say something more about it? Or just add a snappy sentence to conclude this subsection?}

@@

\section{The Case for Paternalism}
\label{exploring}

\subsection{Why does paternalism work in this context?}
\label{why_paternalism}

@@

\paragraph{Learning.} A first potential explanation involves learning. Our experiment introduced a new contract into an environment that had not previously featured commitment; perhaps clients required experience to understand its benefits. Given the strongly positive impact of forcing, this explanation would suggest that clients who were forced once would subsequently choose commitment if given the chance to do so. 
A subset of \hl{XXXX} clients from our sample returned to pawn again on another day before the end of the experiment. Whereas all of the analyses from above restrict attention to the first day on which a given individual pawned, Table \ref{learning_table} presents information about participants' \emph{subsequent} pawning behavior. Column (1) considers the 228 clients who returned to pawn again at a day/branch that was randomly assigned to the choice arm. Each of the two rows in this column presents a difference of mean commitment take-up rates, and associated standard error. The first row compares those who were \emph{initially} assigned to forced commitment against those where were assigned to control; the second row compares those who were initially assigned to the choice commitment arm to those who were assigned to the other two arms. In each case, there is no statistically discernible difference in the rates of commitment take-up. Granted, this is a selected sample because the decision to pawn again is potentially endogenous to the initial treatment allocation. For this reason, Column (2) considers the full sample of \hl{4436} by re-defining the ``outcome variable'' to be an indicator for returning to pawn again at a branch/day when commitment was offered \emph{and} choosing commitment. This composite outcome variable is not subject to the sample selection problem. The comparison in the two rows remains the same: forced commitment versus control in row one and choice commitment versus forced arms in row two. Again, there is no statistically discernible difference in commitment take-up rates in either row. While these exercises cannot completely exclude the possibility that learning plays a role, the provide no indication that the lack of voluntary compliance is simply a matter of inexperience with commitment.

%a subset of 228 clients from our experiment who were exposed to the experiment in one round and then returned to take another loan at a branch where the choice of commitment was offered.  Table \ref{learning_table} shows the results of this analysis.   The first column uses only the (endogenous) sample that took multiple loans, and the second column uses the whole experimental sample and defines the outcome as ``returned and chose commitment''.  While the first column is under-powered, the point estimate is actually negative.  The estimate in the second column is pushed upwards by the positive effect of Forcing on repeat borrowing shown in Table \ref{repeat_loans}, and yet the estimate here is very close to zero.  Hence the window available to us on learning provides little comfort that the lack of voluntary compliance is simply a matter of inexperience with commitment.

%Some people self-select into returning for another loan (endogenous). The people who return are randomized into the same three arms as before. Note that we have *not* used their second visits in any other data analysis so far, so this new data. For the self-selected sub-sample, we estimate the difference in commitment take-up across people who were initially assigned to forced commitment versus control: first row and first column. This is zero. The second row in the first column restricts attention to people who were initially assigned to either the choice or control arms, endogenously returned, and were exogenously assigned to choice a second time. We compare the commitment take-up rates the second time around across people who were initially assigned to choice versus those who were initially assigned to the status quo

%Second column defines an outcome that equals one if and only if you *both* return *and* choose commitment the second time around. (Note that this requires you to have been randomly assigned to choice the second time.) The first row compares people who were assigned at random to commitment the first time around against those who were assigned to control. The second row compares those who were offered a choice the first time around to those who were forced into the status quo contract

\paragraph{Time discounting.} Discounting is a second potential explanation for our results.  Our estimated decrease in the financial cost of credit from above ignores discounting, but the intervention inherently imposes up-front costs (early payment) in return for delayed benefits (recovery of pawn).  Highly impatient individuals might therefore rationally choose the \emph{status quo} contract, despite our results showing a benefit raw (undiscounted) returns.  To investigate this explanation we can calculate the net present value (NPV) of the financial cost $\text{TUT}$ effect under different hypothetical discount rates, given the timing of repayment and pawn recovery. Figure \ref{fc_discount_rates} presents the results of this exercise. We see that non-choosers continue to experience significant decreases in NPV financial costs up to annual discount rates of 4,000\%, and the NPV remains negative, although not significant, at 10,000\% discount rates.  As such, discounting is unlikely to explain why those who benefit, on average, from commitment fail to choose it when offered.

\paragraph{Survey Data.}
The remaining exercises in the paper require information from the intake survey, and hence use only the subset of individuals who responded to the survey. 
Table \label{SS_cond_survet} presents information about survey non-response.
Panel A is a balance table that compares loan amount and day of the week across treatment arms for the subset of borrowers who responded to \hl{at least one survey question}.
The p-values in the fourth column are for the F-test of no difference of means across teratment arms. 
Panel B presents response-rates by question for each arm of the experiment, along with p-values for the F-test of no difference in question-specific response rate across treatment arms. 
While this is a selected sample, estimates of the ATE, TOT, and TUT are nearly identical whether computed from the full sample survey-respondent sub-sample.
In exercises that rely on one survey question, we use the full sample of borrowers who answered that question.
In the random forest exercises that follow, we use data for every borrower who answered at least one survey question.

%\todo[inline]{@Issac: do we have a table of TOT/TUT/ATE results for the sub-sample of survey respondents? We should add this as Table OA-2. What should we take as our sub-sample? We'd like to have this for people who answered \emph{at least} one survey question since those are the people who appear in our random forest exercises. We'd also like to have it for people who answered the time inconsistency question, and for people who answered the sure confidence question. (Each as a separate number)}

\paragraph{Present bias.} If the benefits of commitment among non-choosers cannot be explained by standard models of rational choice, the canonical behavioral story would center on time inconsistency.  While commitment is useful to anyone with hyperbolic time preferences, only those who are sophisticated--i.e.\ aware that they are hyperbolic discounters--will demand it.  A large share of ``na\"ive'' hyperbolics in the population--borrowers who are unaware that they are hyperbolic discounters--could therefore drive a large and positive $\text{TUT}$.  Our baseline survey included standard questions about discount rates between today and a month in the future versus discount rates between three and four months in the future.\footnote{The remaining exercises in the paper require information from the intake survey, and hence use only the subset of individuals who responded to the survey.  While this is a selected sample, estimates of the ATE, TOT, and TUT are nearly identical whether computed from the full sample survey-respondent sub-sample.}  This allows us to classify borrowers who display more impatience over immediate delays as time inconsistent.  This measure of financial hyperbolicity is widely used in survey research, although it is not without problems.\footnote{Our measure is dichotomous, and it is not incentivized. Recent empirical work has shown the superiority of more elaborate measures such as ``convex time budgets'' \citep{andreoni2015measuring} while questioning the interpretation of measures of hyperbolicity that are not based on consumption \citep{andreoni2012estimating, cohen2020measuring}, suggesting that real effort tasks provide a better measure \citep{augenblick2015working}.  Given that we had only a few minutes to interview real pawnshop clients prior to a commercial transaction, our simple measure was a necessary compromise.}

If we could perfectly measure hyperbolicity, we could divide the sample into three groups: sophisticated hyperbolics who chose commitment, time-consistent non-choosers for whom forcing will not be effective, and naive hyperbolic non-choosers for whom it will. If hyperbolic discounting fully explains the low take-up rate of voluntary commitment, this would imply that the forcing effect should arise entirely from hyperbolic non-choosers. If our survey measure divides borrowers into the correct groups, this implication can be checked by estimating the $\text{TUT}$ conditional on hyperbolicity.

\todo[inline]{Among people who answer part of the survey, not all of them answer both the sure confidence and time inconsistency questions. In each of the two exercises below, we use the full sample of people who answered the relevant question. This means that the ``overall'' TUT for each exercise, namely the TUT that we decompose, could be different. Need to think about how to present / discuss this.}

\todo[inline]{We decided to make a picture. The picture will show the overall TUT (for a given survey respondent sub-sample), along with the TUT for $X=0$ and $X = 1$, with SEs for the latter two. The distance from the overall to each ``endpoint'' encodes the share of each group. We want to see if, e.g.\ the $X=1$ group is above the overall TUT while the $X=0$ group is below and indistinguishable from zero.}

\todo[inline]{There are two exercises, and we'll do each one in the same way: present bias and sure confidence. In each case, there's a binary indicator that creates two groups. We want to know if this grouping can ``explain'' the positive TUT. At minimum, should see that effect is concentrated on those with the indicator equal to one. Never totally convincing since there could be an unobserved characteristic that is correlated with our indicator variable. If we had a clean hyperbolicity story, we'd have four strata: rational, time inconsistent and naive, time inconsistent and sophisticated, and a fourth group that chooses commitment despite being time consistent. If time inconsistency is the whole story, the negative TUT should be entirely concentrated on the naive types. In other words, they should have a large positive TUT but everyone else should but everyone else should have something close to zero or negative. In terms of decomposing the TUT, we're already restricting attention to people who would not choose. So when we're looking at the TUT we really only have two of these strata: rational types who are not hyperbolic and don't choose commitment, and types who are hyperbolic and don't choose commitment (naives). So $C=0,X=1$ is naive and $C=0,X=0$ is rational. Should find positive effect for $C=0,X=1$ and zero or negative for $C=0,X=0$. To be clear: the point is that we assume by choosing or not choosing commitment, you reveal whether you are sophisticated or not, given that we know your $X$. First thing we could ask is, among non-choosers how many are ``rational'' versus how many are naive. These are the two probabilities in Eq 12. Second compare the treatment effects. Can do the same thing for sure confidence with a slight caveat that it's harder to use the language ``naive'' or ``rational'' here, but we can still think about it in a similar kind of way as long as we're careful with the language.}

\todo[inline]{This stuff needs to be removed / updated / edited based on the todos listed above.}
For any binary pre-treatment covariate $X_i$, we can calculate the relative contributions of any two groups $X_i=0$ or $X_i=1$ to the overall $\text{TUT}$ effect using the following decomposition: 
\begin{align}
\nonumber
        1=& \frac{\mathbbm{E}[Y_{1i}-Y_{0i} | C_i=0, X_i=1]}{\text{TUT}}\mathbbm{P}(X_i=1 | C_i=0) \\
        \quad &+ \frac{\mathbbm{E}[Y_{1i}-Y_{0i}| C_i=0, X_i=0]}{\text{TUT}}\mathbbm{P}(X_i=0 | C_i=0)
        \label{eq:decomp}
\end{align}
where $\text{TUT}$ is the \emph{overall} treatment on the untreated effect and $\mathbbm{E}[Y_{1i} - Y_{0i}|C_i = 0, X_i = x]$ is the TUT for borrowers with $X_i = x$.    
If, as the behavioral theory outlined above would predict, the $\text{TUT}$ arises solely from hyperbolics then term with $X_i=1$ the former term will be one and the term with $X_i = 0$ will be zero. 
We explore the empirical support for explanation below.
But first we consider a second potential behavioral explanation.

\paragraph{Sure confidence.} While 74\% of control participants believe they have a 100\% chance of recovering their pawn, in reality only \hl{56\%} will go on to do so.  This suggests a market characterized by over-optimism.  Incorrect expectations about recovery probabilities could explain low take-up in that individuals who believe they will repay may, rationally, choose to forgo the costs associated with commitment that are designed to induce repayment.  Hence over-optimistic expectations in recovery probabilities will translate directly into under-adoption of preventive measures.   Similar to our definition of hyperbolicity above, we define a binary attribute we call ``sure-confidence.'' This measure equals one for any individuals who say at the time of borrowing that they have a 100\% probability of recovering their pawn. The same decomposition that we used above in our discussion of hyperbolic discounting, \eqref{eq:decomp}, can be used to explore the extent to which sure confidence explains our positive and significant TUT estimate by redefining the covariate $X_i$.

@@

Figure \ref{tut_beh_partition} shows the relative contributions of present bias and sure-confidence for the $\text{TUT}$.  In each figure the orange bar represents the contribution from those who do not possess the attribute, and the blue bar from those that do.  We see that the forcing effect is localized mostly to those who are \textit{not} time inconsistent, contradicting naive hyperbolicity as the justification for paternalism.  In contrast, sure-confidence being a category that completely isolates the $\text{TUT}$, suggesting that forcing works for those who do not consider repayment structure because they don't think they need it.  Our measure of hyperbolicity is based on unincentivized responses in a short survey and so is likely to be noisy; nonetheless we see no evidence here that it drives the forcing effect.  Rather, this analysis suggests that paternalism is effective in this case is because of a group of overconfident borrowers who, heedless of the possibility of default, do not choose commitment and yet would benefit substantially from receiving it.

If the attribute of ``sure confidence'' proves so important in explaining the TUT, what are its determinants? In Figure \ref{determinants_sure} we plot the coefficient estimates from a regression that explains sure confidence with a battery of individual-level characteristics.  Older males are more likely to be sure confident, as are those with more education.  Taken at face value, the sure confident also appear to face less financial stress, to have less trouble paying bills, and to be more frequently relied upon financially by family members.  However, through a behavioral lens it is also possible that the type of person who is over-confident in their ability to repay a loan also maintains fictions in other domains of their financial life, providing answers to the baseline survey questions that exaggerate their degree of economic security. In any case it appears that sure confidence may be difficult to predict with easily-observed and objective demographic criteria, a point to which we return below.

@@

\todo[inline]{@Frank: note that we for the wide forest we use everyone who answered at least one survey question in the random forests. We have dummies for missingness of any of the predictors. We then take this as ground truth. For the narrow forest, we restrict to the sample for which we don't have missing values. Under certain assumptions, this ``controls'' for selection into the survey. Need to think a bit more about the interpretation here: it's slightly tricky. Question of external validity? Imagine another sample with the same pattern of non-response, then there's probably no concern. I think the issue here relates to whether the covariates that are missing for us would be missing in the hypothetical targeting exercise. It's a question of ``could we have targeted'' versus ``could you target'' in a setting where you have administrative data for everybody?}

@@

 Figure \ref{choose_wrong}, Panel A shows the results of this exercise, reinforcing the general superiority of commitment.  Among choosers, only 18\% would have had superior outcomes had they not complied, whereas among non-choosers almost 80\% made a mistake according to this definition.  Because this arm is comprised of 89\% non-choosers, the overall rate of mistake in the arm was around 68\%.  As we increase the threshold on the size of the mistake necessary to be classified as having made the wrong choice, by definition the share in both groups falls, and among choosers the number making an error falls quite quickly to zero.

@@

Panel C of this figure replicates this exercise for the forced commitment arm, with the difference being that the relevant treatment effect to match is now the ATE of the forced commitment arm.  This allows us to identify the winners and losers from paternalism in a nuanced manner, since members of groups with CATEs$<$0 are hurt and everyone else is helped.  Because the ATE$>$TUT, this exercise results in an even larger fraction of individuals benefiting from commitment; here we find that fully 91\% of individuals are better off being forced into commitment than staying in the control. This now allows us to make a stronger statement in favor of paternalism; not only is the case that forcing commitment generates large benefits on average, but it is also generating benefits for almost 90\% of the forced population.

@@

\begin{table}[H]
\caption{Effects on Financial Cost}
\label{main_impact_table}
\begin{center}
\scriptsize{\input{./Tables/decomposition_main_te.tex}}
\end{center}
\scriptsize This table shows the treatment effects for our core pecuniary outcomes. Each column is a different regression for different outcomes on an indicator for the forced and choice arms, following specification in equation \ref{basic_reg}. Columns (1) \& (7) analyze our core financial cost measures, while the rest of the columns decompose these into finer components as follows:

@@

\textcolor{blue}{A few borrowers have more than one loan. These are treated as different observations, but Table \ref{multiple_loans} shows our results are similar collapsing the data at the person level or using only the assignment of the first loan.} Each regression includes branch and day-of-week FE. Standard errors are clustered at the branch-day level.

@@

\todo[inline]{Enrique deleted subfigure b}
\todo[inline]{should we flip the x-axis, so they look for CDFs?}
